Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2024-11-29 paper.tex
small edit

\section{Multiscale Model}
\label{sec:model}
As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$. In our context, the graph properties, that is the entries $\omega_{ij}$ in the adjacency matrix $\mathbf{W}$, only depends on the HFX values since other modeling parameters are kept consistent.

Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
    \label{equ:Marcus2}
\end{equation}
%
where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation. The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions. 
The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}). 
In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Molecular Dynamics}
The OSC morphology, that is the spacial coordinate of all the atoms, are generated by molecule dynamics. The GROMACS software package~\cite{berendsen_gromacs_1995} is utilized to implement atomistic molecular dynamics simulations of bulk amorphous MADN with the empirical force field obtained via Automated Topology Builder~\cite{stroet_automated_2018}.

>>>>

\section{Multiscale Model}
\label{sec:model}
The multiscale model maps a large scale molecular morphology with atomistic detail into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$, where the set of nodes $\mathbf{V}$ is determined from the center-of-masses of the individual molecules and $\mathbf{W}$ is the adjacency matrix formed by the Marcus rates $\omega_{ij}$. Two nodes $i,j$ are connected if the corresponding molecules have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.

%Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
%
%\begin{equation}
%    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
%    \label{equ:Marcus2}
%\end{equation}
%
%where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation. The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions. 
%The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).

%The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bjoern{STOP}{HERE}

\subsection{Molecular Dynamics}
The OSC morphology, that is the spacial coordinate of all the atoms, are generated by molecule dynamics. The GROMACS software package~\cite{berendsen_gromacs_1995} is utilized to implement atomistic molecular dynamics simulations of bulk amorphous MADN with the empirical force field obtained via Automated Topology Builder~\cite{stroet_automated_2018}.
